Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-12-18 WSSSPE4_report/WSSSPE4_paper.tex
adding PDF of submission, initial version of response letter accepting changes in intro from Anshu removing appendix of organizers and PC

@@

At the workshop, we introduced a Code of Conduct (CoC).%
\footnote{\url{http://wssspe.researchcomputing.org.uk/wssspe4/code-of-conduct/}}
The CoC was conceived for the workshop and a guideline for the community of scientists that WSSSPE
supports, including their personal and online interactions (e.g., on
Twitter, in email lists, in the Slack team). The WSSSPE4 CoC is based on the
FORCE11 conference CoC~\cite{FORCE11:CoC}, which is in turn based on the Code4Lib
CoC~\cite{Code4Lib:CoC}.
The main guidelines of the CoC are:
\begin{quote}
    WSSSPE events are community events intended for networking and collaboration
    as well as learning. We value the participation of every member of the
    community and want all attendees to have an enjoyable and fulfilling
    experience. Accordingly, all attendees are expected to show respect and
    courtesy to other attendees throughout the event and in interactions online
    associated with the event.

@@

    To make clear what is expected, everyone taking part in WSSSPE events and
    discussions---speakers, helpers, organizers, and participants---is required
    to conform to the Code of Conduct, listed on the community website \cite{}.

@@

This paper is a summary of a longer report~\cite{WSSSPE4-report} on the events at the workshop and the submitted materials.
The remainder of the paper includes the call for papers (\S\ref{sec:preworkshop}); the WSSSPE mission and vision (\S\ref{sec:mission}); a set of presentations that included a keynote, papers, lighting talks, and a panel (\S\ref{sec:presentations}); and the activities of a set of working groups (\S\ref{sec:WGs}).  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.
This report also mentions the Slack channel created for further discussions (\S\ref{sec:slack}), and it highlights an attendee survey (\S\ref{sec:survey}) before concluding (\S\ref{sec:conclusions}).
An appendix lists the organizers and program committee members (\S\ref{sec:orgcom}).

@@

\newpage
\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Organization}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\todo{Do we want email addresses here?}

WSSSPE4 organizers were:

{\scriptsize
\begin{longtable}{lll}
\input{orgcom}
\end{longtable}
}

The WSSSPE4 program committee comprised:

{\scriptsize
\begin{longtable}{lll}
\input{program_committee}
\end{longtable}
}

>>>>

\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}
\makeatother

@@

At the workshop, we introduced a Code of Conduct (CoC).%
\footnote{\label{footnote:CoC}\url{http://wssspe.researchcomputing.org.uk/wssspe4/code-of-conduct/}}
The CoC was conceived for the workshop and a guideline for the community of scientists that WSSSPE
supports, including their personal and online interactions (e.g., on
Twitter, in email lists, in the Slack team). The WSSSPE4 CoC is based on the
FORCE11 conference CoC~\cite{FORCE11:CoC}, which is in turn based on the Code4Lib
CoC~\cite{Code4Lib:CoC}.
The main guidelines of the CoC are:
\begin{quote}
    WSSSPE events are community events intended for networking and collaboration
    as well as learning. We value the participation of every member of the
    community and want all attendees to have an enjoyable and fulfilling
    experience. Accordingly, all attendees are expected to show respect and
    courtesy to other attendees throughout the event and in interactions online
    associated with the event.

@@

    To make clear what is expected, everyone taking part in WSSSPE events and
    discussions---speakers, helpers, organizers, and participants---is required
    to conform to the Code of Conduct\footnoteref{footnote:CoC}.

@@

This paper is a summary of a longer report~\cite{WSSSPE4-report} on the events at the workshop and the submitted materials.
The remainder of the paper includes the call for papers (\S\ref{sec:preworkshop}); the WSSSPE mission and vision (\S\ref{sec:mission}); a set of presentations that included a keynote, papers, lighting talks, and a panel (\S\ref{sec:presentations}); and the activities of a set of working groups (\S\ref{sec:WGs}).  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.
This report also mentions the Slack channel created for further discussions (\S\ref{sec:slack}), and it highlights an attendee survey (\S\ref{sec:survey}) before concluding (\S\ref{sec:conclusions}).
%An appendix lists the organizers and program committee members (\S\ref{sec:orgcom}).

@@

%\newpage
%\appendix
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Organization}  \label{sec:orgcom}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\todo{Do we want email addresses here?}
%
%WSSSPE4 organizers were:
%
%{\scriptsize
%\begin{longtable}{lll}
%\input{orgcom}
%\end{longtable}
%}
%
%
%The WSSSPE4 program committee comprised:
%
%{\scriptsize
%\begin{longtable}{lll}
%\input{program_committee}
%\end{longtable}
%}
